### 2012-02-08 docs/SDC/sdc.tex
more sensible step labeling

{\bf Step 1:} ({\it Advance thermodynamic variables}) In this step we integrate $(\rho, \rho X_k, \rho h)$ over the full time step.  We use a predictor-corrector approach, as explained below.\\

{\bf Step 1A:} ({\it Predictor}) In the predictor, we compute an estimate of $(\rho, \rho X_k, \rho h)$ at the new time level to obtain time-advanced values of $S$, $\beta_0$, and transport coefficients that will be used in the corrector.  The quantities $(S, \beta_0, k_{\rm th}, c_p, \xi_k, h_p)^n$ are computed from the the thermodynamic variables at $t^n$.\\

{\bf Step 1A-i:} ({\it Compute advection velocities}) Use $\Ub^n$ and a second-order Godunov method to compute time-centered edge velocities, $\uadvsdcstar$, with a lagged pressure gradient and explicit buoyancy forcing terms.  The $\star$ superscript indicates that this field does not satisfy the divergence constrain.  Compute $S^{n+\myhalf,{\rm pred}}$ by extrapolating in time,
\begin{equation}
S^{n+\myhalf,{\rm pred}} = S^n + \frac{\Delta t^n}{2}\frac{S^n - S^{n-1}}{\Delta t^{n-1}},
\end{equation}
and project $\uadvsdcstar$ to obtain $\uadvsdcpred$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^n\uadvsdcpred\right) = S^{n+\myhalf,\rm{pred}}.
\end{equation}

{\bf Step 1A-ii:} ({\it Compute advective fluxes}) Use $\uadvsdcpred$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf,{\rm pred}}$, with time-lagged reactions, explicitly evaluated diffusion, and a time-centered thermodynamic pressure advective derivative as source terms.\\

{\bf Step 1A-iii:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}}X_{k,{\rm AD}}^{n+1,{\rm pred}} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + I_{R,\rho X_k}^{\rm lagged}.\label{eq:sdc species 2}
\end{equation}
Then, solve a Crank-Nicolson-type diffusion equation for $h^{n+1,{\rm pred}}_{\rm AD}$, using transport coefficients evaluated at $t^n$ everywhere,
\begin{eqnarray}
\frac{\rho^{n+1,{\rm pred}}h^{n+1,{\rm pred}}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + \uadvsdcpred\cdot\nabla p_0 + I_{R,\rho h}^{\rm lagged}\nonumber\\
&& + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n + \nabla\cdot\frac{\kth^n}{c_p^n}\nabla h_{\rm AD}^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_{k,{\rm AD}}^{n+1,{\rm pred}}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0\right)\label{eq:sdc enthalpy 2}
\end{eqnarray}

{\bf Step 1A-iv:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}^{\rm pred}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{R,\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{\rm pred}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{R,\rho h}^{\rm lagged}$ term.  Use VODE to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,{\rm pred}}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{\rm pred} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{\rm pred} + \rho\Hnuc.
\end{eqnarray}

{\bf Step 1B:} ({\it Corrector}) In the corrector, we use the time-advanced state from the predictor to perform a more accurate integration of the thermodynamic variables.  The quantities $(S, \beta_0, k_{\rm th}, c_p, \xi_k, h_p)^{n+1,{\rm pred}}$ are computed from $(\rho,\rho X_k,\rho h)^{n+1,{\rm pred}}$.\\

{\bf Step 1B-i:} ({\it Compute advection velocities}) First, compute $S^{n+\myhalf}$ and $\beta_0^{n+\myhalf}$ using
\begin{equation}
S^{n+\myhalf} = \frac{S^n + S^{n+1,{\rm pred}}}{2}, \qquad \beta_0^{n+\myhalf} = \frac{\beta_0^n + \beta_0^{n+1,{\rm pred}}}{2}
\end{equation}
Then, project $\uadvsdcstar$ to obtain $\uadvsdc$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^{n+\myhalf}\uadvsdc\right) = S^{n+\myhalf}.
\end{equation}

{\bf Step 1B-ii:} ({\it Compute advective fluxes}) Use $\uadvsdc$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf}$, with iteratively-lagged reactions, explicitly evaluated diffusion, and a time-centered thermodynamic pressure advective derivative as source terms.\\

{\bf Step 1B-iii:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1}X_{k,{\rm AD}}^{n+1} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right] + I_{R,\rho X_k}^{\rm pred}.\label{eq:sdc species 3}
\end{equation}
Then, solve a backward-Euler-type correction equation for $h^{n+1}_{\rm AD}$,
\begin{eqnarray}
\frac{\rho^{n+1}h^{n+1}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf}\uadvsdc\right] + \uadvsdc\cdot\nabla p_0 + I_{R,\rho h}^{\rm pred}\nonumber\\
&& + \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1}_{\rm AD} + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n - \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^{n+1,{\rm pred}} k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla X_{k,{\rm AD}}^{n+1}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^{n+1,{\rm pred}}k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla p_0\right)\label{eq:sdc enthalpy 3}
\end{eqnarray}

{\bf Step 1B-iv:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}$ as the right hand side of (\ref{eq:sdc species 3}) without the $I_{R,\rho X_k}^{\rm pred}$ term, and define $Q_{\rho h}$ as the right hand side of (\ref{eq:sdc enthalpy 3}) without the $I_{R,\rho h}^{\rm pred}$ term.  Use VODE to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h} + \rho\Hnuc.
\end{eqnarray}

{\bf Step 2:} ({\it Advance velocity and dynamic pressure})\\

>>>>

The time-advancement is divided into three major steps.  The first step is the predictor, where we integrate the thermodynamic variables over the full time step.  The second step is corrector, where we use the results from the predictor to perform a more accurate temporal integration of the thermodynamic variables.  The third step is the velocity and dynamic pressure update.

{\bf Step 1:} ({\it Predictor}) In this step, we integrate $(\rho, \rho X_k, \rho h)$ over the full time step.  The quantities $(S, \beta_0, k_{\rm th}, c_p, \xi_k, h_p)^n$ are computed from the the thermodynamic variables at $t^n$.  This step is divided into several sub-steps:\\

{\bf Step 1A:} ({\it Compute advection velocities}) Use $\Ub^n$ and a second-order Godunov method to compute time-centered edge velocities, $\uadvsdcstar$, with a time-lagged pressure gradient and explicit buoyancy forcing terms.  The $\star$ superscript indicates that this field does not satisfy the divergence constrain.  Compute $S^{n+\myhalf,{\rm pred}}$ by extrapolating in time,
\begin{equation}
S^{n+\myhalf,{\rm pred}} = S^n + \frac{\Delta t^n}{2}\frac{S^n - S^{n-1}}{\Delta t^{n-1}},
\end{equation}
and project $\uadvsdcstar$ to obtain $\uadvsdcpred$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^n\uadvsdcpred\right) = S^{n+\myhalf,\rm{pred}}.
\end{equation}

{\bf Step 1B:} ({\it Compute advective fluxes}) Use $\uadvsdcpred$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf,{\rm pred}}$, with time-lagged reactions, explicitly evaluated diffusion, and a time-centered thermodynamic pressure advective derivative as source terms.\\

{\bf Step 1C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}}X_{k,{\rm AD}}^{n+1,{\rm pred}} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + I_{R,\rho X_k}^{\rm lagged}.\label{eq:sdc species 2}
\end{equation}
Then, solve a Crank-Nicolson-type diffusion equation for $h^{n+1,{\rm pred}}_{\rm AD}$, using transport coefficients evaluated at $t^n$ everywhere,
\begin{eqnarray}
\frac{\rho^{n+1,{\rm pred}}h^{n+1,{\rm pred}}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + \uadvsdcpred\cdot\nabla p_0 + I_{R,\rho h}^{\rm lagged}\nonumber\\
&& + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n + \nabla\cdot\frac{\kth^n}{c_p^n}\nabla h_{\rm AD}^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_{k,{\rm AD}}^{n+1,{\rm pred}}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0\right)\label{eq:sdc enthalpy 2}
\end{eqnarray}

{\bf Step 1D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}^{\rm pred}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{R,\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{\rm pred}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{R,\rho h}^{\rm lagged}$ term.  Use VODE to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,{\rm pred}}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{\rm pred} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{\rm pred} + \rho\Hnuc.
\end{eqnarray}

{\bf Step 2:} ({\it Corrector}) In the corrector, we use the time-advanced state from the predictor to perform a more accurate integration of the thermodynamic variables.  The quantities $(S, \beta_0, k_{\rm th}, c_p, \xi_k, h_p)^{n+1,{\rm pred}}$ are computed from $(\rho,\rho X_k,\rho h)^{n+1,{\rm pred}}$.  This step is divided into several sub-steps:\\\\

{\bf Step 2A:} ({\it Compute advection velocities}) First, compute $S^{n+\myhalf}$ and $\beta_0^{n+\myhalf}$ using
\begin{equation}
S^{n+\myhalf} = \frac{S^n + S^{n+1,{\rm pred}}}{2}, \qquad \beta_0^{n+\myhalf} = \frac{\beta_0^n + \beta_0^{n+1,{\rm pred}}}{2}
\end{equation}
Then, project $\uadvsdcstar$ to obtain $\uadvsdc$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^{n+\myhalf}\uadvsdc\right) = S^{n+\myhalf}.
\end{equation}

{\bf Step 2B:} ({\it Compute advective fluxes}) Use $\uadvsdc$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf}$, with iteratively-lagged reactions, explicitly evaluated diffusion, and a time-centered thermodynamic pressure advective derivative as source terms.\\

{\bf Step 2C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1}X_{k,{\rm AD}}^{n+1} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right] + I_{R,\rho X_k}^{\rm pred}.\label{eq:sdc species 3}
\end{equation}
Then, solve a backward-Euler-type correction equation for $h^{n+1}_{\rm AD}$,
\begin{eqnarray}
\frac{\rho^{n+1}h^{n+1}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf}\uadvsdc\right] + \uadvsdc\cdot\nabla p_0 + I_{R,\rho h}^{\rm pred}\nonumber\\
&& + \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1}_{\rm AD} + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n - \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^{n+1,{\rm pred}} k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla X_{k,{\rm AD}}^{n+1}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^{n+1,{\rm pred}}k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla p_0\right)\label{eq:sdc enthalpy 3}
\end{eqnarray}

{\bf Step 2D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}$ as the right hand side of (\ref{eq:sdc species 3}) without the $I_{R,\rho X_k}^{\rm pred}$ term, and define $Q_{\rho h}$ as the right hand side of (\ref{eq:sdc enthalpy 3}) without the $I_{R,\rho h}^{\rm pred}$ term.  Use VODE to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h} + \rho\Hnuc.
\end{eqnarray}

{\bf Step 3:} ({\it Advance velocity and dynamic pressure})\\
